---
title: "RDD"
author:
- chengkan_tao
- ~
- ~
documentclass: ctexart
output: rticles::ctex
keywords:
- 中文
- R Markdown
---
```{r eval=FALSE}
devtools::install_github(c('rstudio/rmarkdown', 'yihui/tinytex'))
tinytex::install_tinytex()
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# abstract

The author tries to find the effect of punishments and deterrence on driving under
the influence (DUI) through administrative records on 512,964 DUI BAC tests in the 
state of Washington from 1995 to 2011 by discontinuity approach. Blood alcohol content 
and previous offenses in the data set are used to estimate the effect.
This paper finds having a BAC above either DUI or aggravated DUI threshold reduces repeat drunk
driving. Having a BAC over the 0.08 DUI threshold is associated with a about 2 percent point 
decline in recidivism over the next four years. And, having a BAC over the 0.15 DUI will leads to about 3 percentage point decline in recidivism.


```{r, include=FALSE}


library(haven)
library(tidyverse)
library(stargazer)
library(estimatr)
library(reshape)
library(rdd)
library(rdrobust)
library(rddensity)
library(tidyfst)
library(ggplot2)
library(texreg)
library(sandwich)
library(KernSmooth)
hansen_dwi <- read.csv("~/GitHub/CAUSAL INFERENCE CLASS/causal-inference-class/Data/hansen_dwi.csv", header=TRUE)

```
# read data off-line

# Q3
```{r, fig.cap='Q3'}
BAC = hansen_dwi %>%
  mutate_vars(.cols = bac1, .func = function(bac1) ifelse(bac1<0.08,0,1))
BAC = data.frame(BAC,hansen_dwi$bac1)
BAC = rename(BAC,c(bac1="DUI"))
BAC = rename(BAC,c(hansen_dwi.bac1="bac1"))
```


# Q4
```{r, fig.cap='Q4'}
rdr = rdrobust(y = hansen_dwi$recidivism,x=hansen_dwi$bac1, c = 0.08)
summary(rdr)

ggplot(data = hansen_dwi,mapping = aes(bac1)) + 
  geom_histogram(binwidth = 0.001, fill = "lightblue", colour = "black") + 
  labs(title = 'BAC Histogram', y = 'Frequency', x = 'bac1')
```
To see if there’s any evidence for manipulation, we would use density test. Through the 
picture, I cannot find a obvious discontinuity.

# Q5
```{r, fig.cap='Q5'}
lm_q5_male <- lm_robust(male ~ DUI+bac1+bac1*DUI, data = BAC)
coef(lm_q5_male)

lm_q5_white <- lm_robust(white ~ DUI+bac1+bac1*DUI, data = BAC)
coef(lm_q5_white)

lm_q5_acc <- lm_robust(acc ~ DUI+bac1+bac1*DUI, data = BAC)
coef(lm_q5_acc)

texreg::screenreg(list(lm_q5_male,lm_q5_white,lm_q5_acc),type="text")
```
They are stable across the DUI punishment thresholds. The coefficients
are not statistically significant.

# Q6
```{r, include=FALSE}
Q6 <- BAC %>% 
  mutate(gg_group = case_when(bac1 > 0.08 ~ 1, TRUE ~ 0))
```

```{r, fig.cap='Q6'}
ggplot(Q6, aes(bac1, acc)) +
  geom_point(aes(x = bac1, y = acc), data = Q6) +
  labs(title = 'Panal A', y = 'accident', x = 'bac1') +
  stat_smooth(aes(bac1, acc, group = gg_group), method = "lm") +
  xlim(0,0.5) + ylim(0,1) +
  geom_vline(xintercept = 0.08)

ggplot(Q6, aes(bac1, acc)) +
  geom_point(aes(x = bac1, y = acc), data = Q6) + 
  labs(title = 'Panal A Quadratic', y = 'accident', x = 'bac1')+
  stat_smooth(aes(bac1, acc, group = gg_group), method = "lm", 
              formula = y ~ x + I(x^2)) +
  xlim(0,0.5) + ylim(0,1) +
  geom_vline(xintercept = 0.08)

ggplot(Q6, aes(bac1, male)) +
  geom_point(aes(x = bac1, y = male), data = Q6) +
  labs(title = 'Panal B', y = 'male', x = 'bac1') +
  stat_smooth(aes(bac1, male, group = gg_group), method = "lm") +
  xlim(0,0.5) + ylim(0,1) +
  geom_vline(xintercept = 0.08)

ggplot(Q6, aes(bac1, male)) +
  geom_point(aes(x = bac1, y = male), data = Q6) + 
  labs(title = 'Panal B Quadratic', y = 'male', x = 'bac1')+
  stat_smooth(aes(bac1, male, group = gg_group), method = "lm", 
              formula = y ~ x + I(x^2)) +
  xlim(0,0.5) + ylim(0,1) +
  geom_vline(xintercept = 0.08)

ggplot(Q6, aes(bac1, aged)) +
  geom_point(aes(x = bac1, y = aged), data = Q6) +
  labs(title = 'Panal C', y = 'aged', x = 'bac1') +
  stat_smooth(aes(bac1, aged, group = gg_group), method = "lm") +
  xlim(0,0.5) + ylim(0,80) +
  geom_vline(xintercept = 0.08)

ggplot(Q6, aes(bac1, aged)) +
  geom_point(aes(x = bac1, y = aged), data = Q6) + 
  labs(title = 'Panal C Quadratic', y = 'aged', x = 'bac1')+
  stat_smooth(aes(bac1, aged, group = gg_group), method = "lm", 
              formula = y ~ x + I(x^2)) +
  xlim(0,1) + ylim(0,80) +
  geom_vline(xintercept = 0.08)

ggplot(Q6, aes(bac1, white)) +
  geom_point(aes(x = bac1, y = white), data = Q6) +
  labs(title = 'Panal D', y = 'white', x = 'bac1') +
  stat_smooth(aes(bac1, white, group = gg_group), method = "lm") +
  xlim(0,1) + ylim(0,1) +
  geom_vline(xintercept = 0.08)

ggplot(Q6, aes(bac1, white)) +
  geom_point(aes(x = bac1, y = white), data = Q6) + 
  labs(title = 'Panal D Quadratic', y = 'white', x = 'bac1')+
  stat_smooth(aes(bac1, white, group = gg_group), method = "lm", 
              formula = y ~ x + I(x^2)) +
  xlim(0,1) + ylim(0,1) +
  geom_vline(xintercept = 0.08)
```
Through these figures, I find these predetermined characteristics remain unchanged
across the punishment thresholds. It's same with what hansen has found.

# Q7
# simple linear regression. I try to use loess(), but I find texreg::screenreg() cannot show the results
```{r, include=FALSE}
Q7_wide = BAC %>% 
  filter(bac1 > .03 & bac1 < 0.13) %>%
  mutate(bac1_sq = bac1^2)
```

```{r, fig.cap='Q7(wide)'}
lm_q7_wide1 = lm_robust(recidivism ~ bac1, data = Q7_wide)
coef(lm_q7_wide1)

lm_q7_wide2 = lm_robust(recidivism ~ bac1*DUI, data = Q7_wide)
coef(lm_q7_wide2)

lm_q7_wide3 = lm_robust(recidivism ~ bac1*DUI+bac1_sq*DUI, data = Q7_wide)
coef(lm_q7_wide3)
```

```{r, include=FALSE}
Q7_narrow = BAC %>% 
  filter(bac1 > 0.055 & bac1 < 0.105) %>%
  mutate(bac1_sq = bac1^2)
```

```{r, fig.cap='Q7(narrow)'}
lm_q7_narrow1 = lm_robust(recidivism ~ bac1, data = Q7_narrow)
coef(lm_q7_narrow1)

lm_q7_narrow2  = lm_robust(recidivism ~ bac1*DUI, data = Q7_narrow)
coef(lm_q7_narrow2)

lm_q7_narrow3  = lm_robust(recidivism ~ bac1*DUI + bac1_sq*DUI, data = Q7_narrow)
coef(lm_q7_narrow3)
```

```{r, fig.cap='Q7(texreg)'}
texreg::screenreg(list(lm_q7_wide1,lm_q7_wide2,lm_q7_wide3),type="text")
texreg::screenreg(list(lm_q7_narrow1,lm_q7_narrow2,lm_q7_narrow3),type="text")
```

# Q8
```{r, include=FALSE}
Q8 = BAC %>% 
  filter(bac1 < 0.15) %>%
  mutate(gg_group = case_when(bac1 > 0.08 ~ 1, TRUE ~ 0))
```

```{r, fig.cap='Q8'}
ggplot(Q8, aes(bac1, recidivism)) +
  geom_point(aes(x = bac1, y = recidivism), data = Q8) +
  stat_smooth(aes(bac1, recidivism, group = gg_group), method = "lm") +
  xlim(0,0.15) + ylim(0,1) +
  geom_vline(xintercept = 0.08)

ggplot(Q8, aes(bac1, recidivism)) +
  geom_point(aes(x = bac1, y = recidivism), data = Q8) +
  stat_smooth(aes(bac1, recidivism, group = gg_group), method = "lm",
              formula = y ~ x + I(x^2)) +
  xlim(0,0.15) + ylim(0,1) +
  geom_vline(xintercept = 0.08)
```

# Q9

Regression discontinuity design gives causal effect of treatment on the outcome.
In this exercise, I use BAC=0.08 as a cutoff and use density test to find whether 
agents can manipulate running variable score. By recreating Table 2 and Figure, 
I fail to reject the null hypothesis that predetermined characters are unrelated 
to DUI. That's the same with hansen's paper.





